Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

Processor, an algorithm (software), and memory are the trio of computation. Memory is organized by the programming languages and developers can control the life of data allocated in the memory. In this thesis, we abstract all data allocated in the memory as an object. In general, we define an object as any block of memory that saves any information in the memory and be able to point to another piece of memory by address. Most of the programming supports dynamic memory allocation. To organize memory better, programming languages divide available memory into three types. 
\begin {comment}
All programming languages are designed to perform complex computations. Computation contains three main ingredients : Processing unit, algorithm, and memory. Processing unit i.e., the processor is the unit which performs arithmetic, and logical operations required. Algorithm dictates the sequence of operation to performed on the data to get the desired output. Algorithm implemented in a programming language is usually referred as program and collection of programs are called software. Memory saves the input, intermediate results and final output of the computation. 
In this thesis, we are more concerned with object-oriented programming languages and object represents user-defined dynamically allocated data. Developers write algorithms in a specific programming language. Programming language organizes the memory consumed by the algorithm. Modern programming languages use three different memories to organize it.
\end{comment} 
They are stack, static and heap memory. The static memory contains all the global variables used by the program. Stack memory is used to manage static(fixed size) allocation of the object whose scope is well defined. Heap memory is used to manage the dynamically allocated objects which usually has infinite scope unless until mentioned by developers.

>>>>

A processor, an algorithm (software), and memory are the trio of computation. Memory is organized by the programming languages and developers to control the life of data. In this thesis, we abstract all data allocated in memory as objects. In general, we define an object as any block of memory that saves information and may contain address of other objects. Most of the programming supports dynamic memory allocation. To organize memory better, programming languages divide available memory into three types. 
\begin {comment}
All programming languages are designed to perform complex computations. Computation contains three main ingredients : Processing unit, algorithm, and memory. Processing unit i.e., the processor is the unit which performs arithmetic, and logical operations required. Algorithm dictates the sequence of operation to performed on the data to get the desired output. Algorithm implemented in a programming language is usually referred as program and collection of programs are called software. Memory saves the input, intermediate results and final output of the computation. 
In this thesis, we are more concerned with object-oriented programming languages and object represents user-defined dynamically allocated data. Developers write algorithms in a specific programming language. Programming language organizes the memory consumed by the algorithm. Modern programming languages use three different memories to organize it.
\end{comment} 
They are stack, static and heap memory. The static memory contains all the global variables used by the program. Stack memory is used to manage static(fixed size) allocation of the object whose scope is well defined. Heap memory is used to manage the dynamically allocated objects which usually has infinite scope unless until mentioned by developers.
